Empirical Bayes analysis of \RNAseq{} data for detection of gene expression heterosis

### 2015-05-28 ebayes_rnaseq_heterosis.tex
laplace

We found MAP estimates for both the independence and dependence models as shown in Table \ref{t:map}. 
\input{include/map}
The MAP estimates for the hierarchical means, $\eta$, and standard deviations, $\sigma$, are consistent between the independence and dependence models with, perhaps, a slightly larger mean and smaller standard deviation for the logarithm of the overdispersion parameter, $\psi_g$, in the dependence model relative to the independence model. In the dependence model, there appears to be high correlation amongst $\mu_{g1}$, $\mu_{g2}$, and $\mu_{g3}$, and negative correlation between $\psi_g$ and each of $\mu_{g1}$, $\mu_{g2}$, and $\mu_{g3}$. The normalization factors, and their variance, are consistent between the two models, with the estimates for the dependence model being consistently 0.02 larger than the estimates for the independence model, and both indicating that there is about a 25\% increase in counts between the least and most thoroughly sequenced samples.

>>>>

We found MAP estimates for both the independence and dependence models as shown in Table \ref{t:map}. 
\input{include/map-laplace}
The MAP estimates for the hierarchical means, $\eta$, and standard deviations, $\sigma$, are consistent between the independence and dependence models with, perhaps, a slightly larger mean and smaller standard deviation for the logarithm of the overdispersion parameter, $\psi_g$, in the dependence model relative to the independence model. In the dependence model, there appears to be high correlation amongst $\mu_{g1}$, $\mu_{g2}$, and $\mu_{g3}$, and negative correlation between $\psi_g$ and each of $\mu_{g1}$, $\mu_{g2}$, and $\mu_{g3}$. The normalization factors, and their variance, are consistent between the two models, with the estimates for the dependence model being consistently 0.02 larger than the estimates for the independence model, and both indicating that there is about a 25\% increase in counts between the least and most thoroughly sequenced samples.
